Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-09 paper.tex
Mostly done with the case studies

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\keywords{Bigraphs \and Probabilistic semantics \and Markov decision process.}
\end{abstract}

@@

From \cite{dblp:journals/tcs/sevegnanic15}.
From PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}

@@

@@

\begin{proposition}
  Any MDP can be expressed as an NBRS.
\end{proposition}
\begin{proof}
  Obvious.
\end{proof}

@@

Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe \cite{koenig1998xavier}.

@@

% TODO: what is a link, mention that it's a hyperedge (at least one node)
Grid layout (but could be any nodes-and-edges layout, as long as it's clear how
to go back home). Tracking visited/unvisited states. Each unvisited state has a
probability $p$ of containing an object. The agent returns (and stays) home
after collecting a set number of objects (easily customisable). Starting at the
bottom left cell.

@@

Lastly, we have three actions for after the agent acquires the specified number
of objects: two for going home west or south (since these are the two directions
necessary and sufficient to reach home), and one for staying home. The
former type of actions have two reaction rules each, depending on whether the
destination cell is visited or not. They are just like the rules in Listing
\ref{agent1_north}, except every mention of \texttt{Agent} is replaced with
\texttt{goal}. The rule to stay home is quite straightforward and is in
Listing \ref{agent1_home}.

@@

@@

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
\usepackage{siunitx}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\keywords{Bigraphs \and Bigraphical Reactive Systems \and Probabilistic
  semantics \and Markov decision process.}
\end{abstract}

@@

% TODO: introduce bigrapher
From \cite{dblp:journals/tcs/sevegnanic15}.
From PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}

@@

Lastly, BigraphER supports \emph{rule priorities}
\cite{DBLP:journals/tcs/BaetenBKW89}, i.e., a partial ordering on the reaction
rules, where a rule of lower priority can be applied only if no rule of higher
priority is applicable. Priorities are implemented by assigning each reaction
rule to a \emph{priority class}, where all classes are strictly ordered, and
reaction rules in the same class have the same priority.

@@

@@

% TODO: Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe \cite{koenig1998xavier}.

@@

% TODO: what is a link, mention that it's a hyperedge (at least one node)
% TODO: explain the syntax of the language
Our first scenario is concerned with collecting objects in a grid-like
two-dimensional world. The agent starts in the southwest corner of the map
(which we call \emph{home}), explores the environment until it collects a
specified number of objects, and returns home (while possibly collecting more
objects along the way). The model tracks which cells of the grid have been
explored, and only the unexplored cells have a constant probability $p$ of
rewarding the agent with an object. The desired number of objects can be easily
changed, and the map can be customised to make some transitions unavailable
(i.e. add walls), as long as the agent can still return home.

@@

Lastly, we have three actions for when the agent acquires the specified number
of objects: two for going home west or south (since these are the two directions
necessary and sufficient to reach home), and one for staying home. The two
actions for going home have two reaction rules each, depending on whether the
destination cell is visited or not. They are just like the rules in Listing
\ref{agent1_north}, except every mention of \texttt{Agent} is replaced with
\texttt{goal}. The rule to stay home simply says that if the agent has achieved
the goal, and is home (characterised by a \texttt{Cell} with only two
directions: \texttt{North} and \texttt{East}), then nothing should change (see
Listing \ref{agent1_home}). To make the agent start heading home as soon as
enough objects are collected, all five reaction rules related to going and
staying home are in a higher priority class.

@@

% TODO: Must mention: \cite{DBLP:conf/giscience/WaltonW12}.

Our second model explores two important concepts in modelling the topology of
space: nesting and uncertainty. Nesting is the idea that spaces can be inside
other spaces: rooms inside floors, floors inside buildings, buildings inside
streets, etc. A key characteristic of nested spaces is that there is a separate
action (or several) taking you from the outer space to the inner space or vice
versa (e.g., using a door to enter or leave a room). In the rest of the paper,
whenever we discuss one space inside another, we will refer to the inner space
as the \emph{room}.

The other concept explored in this section is uncertainty about the topology
itself, i.e., is the door open or closed? The implementation of this idea is
tied to that of rooms: the inside of a room is not defined until the outer cell
encompassing the room (i.e., the area where the door is located) is entered.
Then, the contents of the room are chosen from a finite set of possibilities
with a set probability distribution. After that, the room stays fixed. This
design decision supports the reality of missions with a reasonably short
duration: if the agent finds a locked door, it should not keep revisiting the
door hoping for it to suddenly be open.

As the ideas of collecting objects and tracking visited cells have been
explored already, they are dropped from this model to simplify the
implementation. The goal can simply be defined as moving from one location to
another. We add one extra control, \texttt{Node}. While \texttt{Cell} can be
imagined as a discrete patch of space (e.g., \SI{1}{\square\metre}),
\texttt{Node} can be thought of as a room. While we stick to two layers
(corridors and rooms) in this example, rooms can be freely nested: a room can
contain any number of rooms, each of which can contain more rooms.

\begin{figure}
  \centering
  \includegraphics{models/agent2/nesting_example/example.pdf}
  \caption{The bigraphical structure behind nesting.}
  \label{agent2_nesting}
\end{figure}

@@

In order to impement nesting, a \texttt{Cell} contains a \texttt{Node}, which
can have any number of \texttt{Cell}s of its own. Since after entering a room,
you end up in a specific place inside the room (next to the door), we also need
to link up the \texttt{Node} with one of the \texttt{Cell}s it contains (see
Fig. \ref{agent2_nesting}). Both \texttt{Cell}s and \texttt{Node}s support
having a single link for exactly this purpose. Thus, most of the \texttt{Cell}
ports are not linked to anything, which is implemented via closures (e.g.
\texttt{/x Cell\{x\}}). The initial map in Listing \ref{agent2_initial} has a
corridor of three cells, with the agent on the west-most cell, and a door to a
room in the middle cell. One moves in and out of a room via a pair of actions
with reaction rules pictured in Fig. \ref{go_in_out}.

@@

\lstinputlisting[caption={The action of going north.}, captionpos=b,
language=Big, label=agent2_north, firstline=66,
lastline=75]{models/agent2/agent.big}

The room is a $2 \times 2$ grid of \texttt{Cell}s, which is generated when the
\texttt{Agent} gets to a \texttt{Cell} with an empty \texttt{Node} (represented
by \texttt{Node\{n\}.1}). In order for this to happen before any other action
can take place, the two reaction rules in Listing \ref{agent2_room} are put on a
higher priority class. With probability $p$, the generated room has each
\texttt{Cell} linked to its two neighbours; and with probability $1-p$, the top
two \texttt{Cell}s are not linked , possibly forcing the agent to choose a
different path. Finally, we have four actions, each with a single reaction rule
with probability $1$, corresponding to the four possible directions of travel.
The reaction rules are very similar to those of our previous example, see
Listing \ref{agent2_north}.
